---
title: "ICON8002 SNA"
date: '`r format(Sys.Date())`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=25, fig.height=25, echo = F)
```

# Social Network Analysis
This is a report generated from social network analysis of the actors within the shrimping industry on the Georgia Coast. The resulting output of the analysis demonstrates the relationships between shrimpers, dockers, and other agencies/organizations. 


## Network attributes

* Diameter
```{r}
diameter
```

* Reciprocity
```{r}
reciprocity
```
* Number of edges
```{r}
ecount
```
* Number of egos
```{r}
vcount
```
* Edge density
```{r}
edge_density
```

## Vertex attributes

* Closeness

The vertex with the greatest closeness is $`r as.character(vertex_df$ego[Closeness_max_stat_indiv])`$ (number: $`r Closeness_max_stat_indiv`$). This measures how many steps is required to access every other vertex from a given vertex.

The vertex with the least closeness is $`r as.character(vertex_df$ego[Closeness_min_stat_indiv])`$ (number: $`r Closeness_min_stat_indiv`$). This measures how many steps is required to access every other vertex from a given vertex.

* Degree

The vertex with the greatest degree is $`r as.character(vertex_df$ego[Degree_max_stat_indiv])`$ (number: $`r Degree_max_stat_indiv`$). This measure is the number of its adjacent edges.

The vertex with the fewest degree is $`r as.character(vertex_df$ego[Degree_min_stat_indiv])`$ (number: $`r  Degree_min_stat_indiv`$). This measure is the number of its adjacent edges.




## Network plots

```{r fig.cap=paste("Original social network plot with no alterations (Fruchterman-Reingold layout)")}
plot(graph_complete_simpl,
          layout = layout.fruchterman.reingold,
          #edge.color=edge_test$connection,
          edge.arrow.size=.1,
          #vertex.color=profession.colors,
          #vertex.size=((in.degree)*1.5),
          vertex.size=5,
          vertex.label=NA,
          vertex.label.cex=0.7,
          vertex.label.dist=1,
          vertex.label.degree=-0.6,
          #main="Network Plot",
          #frame=TRUE,
          margin=0.0001)

```

```{r fig.cap=paste("Original social network plot with no alterations (Nicely layout)")}
  plot(graph_complete_simpl,
       #edge.color=edge_test$connection,
       edge.arrow.size=.1,
       #vertex.color=profession.colors,
       #vertex.size=((in.degree)*1.5),
       vertex.size=5,
       vertex.label=NA,
       vertex.label.cex=0.7,
       vertex.label.dist=1,
       vertex.label.degree=-0.6,
       #main="Network Plot_Nicely",
       #frame=TRUE,
       margin=0.0001,
       layout = layout_nicely)
```

```{r fig.cap=paste("Social network plot with vertex colored based on profession (Nicely layout)")}
  plot(graph_complete_simpl,
       layout = layout.graph,
       rescale = F,
       #edge.color=edge_test$connection,
       edge.arrow.size=.1,
       vertex.color=profession.colors,
       #vertex.size=((in.degree)*1.5),
       vertex.size=5,
       vertex.label=NA,
       vertex.label.cex=0.5,
       vertex.label.dist=1,
       vertex.label.degree=-0.6,
       #main="SNA by Profession",
       #frame=TRUE,
       margin = 0.0001)
  
  legend(x=-1.5, y = -0.85, legend = levels(vertex_df$profession.df), 
         col = colr.palette, pch=19, pt.cex=0.8, cex=0.8, bty="n", ncol=1)
  ```